Increasing productivity amid stable nutrient regmines in Rhode Island Lakes and Reservoirs

### 2019-11-05 nalms_2019_talk/increasing_chla_stable_nutrients_talk.Rmd
outline and draft of slide 1 done

## Nutrients and Productivity
::::::::::::::{.columns}
:::{.column}
- Nutrients drive growth
- One goal is to reduce increased phyto
- Long-term data needed
:::
:::{.column}

@@

- What has happened with P and N reductions?
- What 
- Did it work?

>>>>

## What drives lake productivity
::::::::::::::{.columns}
:::{.column}
- Nutrients
- Temperature
- Other things
:::
:::{.column}

@@

- One goal is to reduce increased phyto
- What has happened with P and N reductions?
- Did it work?
  - Long-term data needed
